Supplemental data to ``\emph{k}-mer-based GWAS enhances causal variant and candidate gene discovery in soybean''

### 2023-03-28 additional_files/main_text.tex
Make a few changes; version submitted to biorxiv

@@

\begin{description}
	\item[Additional file 1.pdf] Supplemental methods and results,
		including Tables \ref{signals_table} to \ref{MATURITY.GROUP_gwas_table}
		and Figures \ref{flower_color_manhattan} to \ref{protein_manhattan}
		(PDF 12.2 MB)
	\item[Additional file 2.csv] Metadata on the sequencing runs retrieved
		from the Sequence Read Archive (SRA) (CSV 71 KB)
	\item[Additional file 3.csv] Metadata on individual accessions following mapping
		and comparison to SoySNP50K data (CSV 36KB)
	\item[Additional file 4.csv] Phenotypic dataset used for GWAS analyses (CSV 135
		KB)
\end{description}

>>>>

\textbf{Contact}: marc-andre.lemay.2@ulaval.ca, francois.belzile@fsaa.ulaval.ca

@@

\begin{description}
	\item[Additional file 1.pdf] Supplemental methods and results,
		including Tables \ref{signals_table} to \ref{MATURITY.GROUP_gwas_table}
		and Figures \ref{flower_color_manhattan} to \ref{protein_manhattan}
		(PDF 12.9 MB)
	\item[Additional file 2.csv] Metadata on the sequencing runs retrieved
		from the Sequence Read Archive (SRA) (CSV 71 KB)
	\item[Additional file 3.csv] Metadata on individual accessions following mapping
		and comparison to SoySNP50K data (CSV 36KB)
	\item[Additional file 4.csv] Phenotypic dataset used for GWAS analyses (CSV 135
		KB)
\end{description}
